Inferring the gravitational potential of the Milky Way with a few precisely measured stars

### 2014-03-15 text/paper2/ms.tex
more minor changes to text

We first test the model using eight stars sampled from the $2.5\times10^8~M_\odot$ simulation (Section~\ref{sec:sims}) --- four from the leading trail, and four from the trailing tail --- assuming perfect observational data for both the stars and the progenitor. The stars are additionally required to be within $50~kpc$ of the Sun. Figure~\ref{fig:} (left panel) shows a sample of stream particles (black) and the eight randomly chosen stars (blue) in the Galactic X-Z plane. We leave the potential parameters --- $q_1$, $q_z$, $\phi$, and $\vhalo$ --- free to vary, along with the Lagrange point offset, $\Loffset$, the tail assignment for each star, $\tailbit^{(i)}$, and probability that each star was shocked, $\pshock^{(i)}$. Figure~\ref{fig:} shows the posterior distribution for the four potential parameters, marginalized over the other parameters.

>>>>

We first test the model using eight stars --- four from the leading trail, and four from the trailing tail --- sampled from the $2.5\times10^8~M_\odot$ simulation (Section~\ref{sec:sims}) assuming perfect observational data for both the stars and the progenitor. The stars were required to be within $50$ kpc of the Sun. Figure~\ref{fig:} (left panel) shows a sample of stream particles (black) and the eight randomly chosen stars (blue) in the Galactic X-Z plane. We leave the potential parameters --- $q_1$, $q_z$, $\phi$, and $\vhalo$ --- free to vary, along with the Lagrange point offset, $\Loffset$, the tail assignment for each star, $\tailbit^{(i)}$, and probability that each star was shocked, $\pshock^{(i)}$. Figure~\ref{fig:} shows the posterior distribution for the four potential parameters, marginalized over the other parameters.

[Interpret the posterior]
